---
output: github_document
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->


<!-- -->
<!-- FILL OUT OPTIONS !!! -->
<!-- -->
```{r scaffolding options, include=FALSE}
github_user_name   <- "petermeissner"
codecov_user_name  <- github_user_name
travis_user_name   <- github_user_name
appveyor_user_name <- github_user_name
```
<!-- -->
<!-- -->




```{r knitr options, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "man/figures/README-"
)
```


```{r r options, include=FALSE}
options("width"=110)

# get package info
tmp <- packageDescription( "caldav" )
#tmp <- packageDescription( basename(getwd()) )

package_name <- tmp$Package

```

```{r readme title, results='asis', echo=FALSE}
cat("#", tmp$Title)
```




**Status**


<a href="https://travis-ci.org/`r travis_user_name`/`r package_name`"><img src="https://api.travis-ci.org/`r github_user_name`/`r package_name`.svg?branch=master"><a/>
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/`r github_user_name`/`r package_name`?branch=master&svg=true)](https://ci.appveyor.com/project/`r github_user_name`/`r package_name`)
<a href="https://codecov.io/gh/`r github_user_name`/`r package_name`"><img src="https://codecov.io/gh/`r codecov_user_name`/`r package_name`/branch/master/graph/badge.svg" alt="Codecov" /></a>
<a href="https://cran.r-project.org/package=`r package_name`">
<img src="http://www.r-pkg.org/badges/version/`r package_name`">
</a>
<img src="http://cranlogs.r-pkg.org/badges/grand-total/`r package_name`">
<img src="http://cranlogs.r-pkg.org/badges/`r package_name`">






```{r, include=FALSE}
filelist.R   <- list.files("R", recursive = TRUE, pattern="\\.R$", ignore.case = TRUE, full.names = TRUE)
filelist.tests   <- list.files("tests", recursive = TRUE, pattern="\\.R$", ignore.case = TRUE, full.names = TRUE)
filelist.cpp <- list.files("src", recursive = TRUE, pattern="\\.cpp$", ignore.case = TRUE, full.names = TRUE)
lines.R      <- unlist(lapply(filelist.R, readLines))
lines.tests  <- unlist(lapply(filelist.tests, readLines))
lines.cpp    <- unlist(lapply(filelist.cpp, readLines))
length.R     <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.R,  value = TRUE, invert = TRUE))
length.tests <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.tests,  value = TRUE, invert = TRUE))
length.cpp   <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.cpp,  value = TRUE, invert = TRUE))
```


*lines of R code:* `r length.R`, *lines of test code:* `r length.tests`



**Version**

```{r, include=FALSE}
source_files <-
  grep(
    "/R/|/src/|/tests/",
    list.files(recursive = TRUE, full.names = TRUE),
    value = TRUE
  )
last_change <-
  as.character(
    format(max(file.info(source_files)$mtime), tz="UTC")
  )
```


```{r, results='asis', echo=FALSE}
cat(tmp$Version, "(",last_change,")")
```

**Description**


```{r, results='asis', echo=FALSE}
cat(tmp$Description)
```


**License**

```{r, results='asis', echo=FALSE}
cat(tmp$License, "<br>")
cat(tmp$Author)
```



**Citation**


```{r, results='asis', echo=FALSE}
cat("```r\n")
cat("citation(\"",package_name,"\")", sep = "")
cat("\n```\n")
```

```{r, results='asis', echo=FALSE}
cat("```r\n")
print_text <- capture.output(print(citation(package_name), style = "text"))
cat(gsub("_", "", print_text))
cat("\n```\n")
```


**BibTex for citing**

```{r, results='asis', echo=FALSE}
cat("```r\n")
cat("toBibtex(citation(\"",package_name,"\"))", sep = "")
cat("\n```\n")
```

```{r, results='asis', echo=FALSE}
cat("```\n")
cat(as.character(toBibtex(citation(package_name))), sep = "\n")
cat("\n```\n")
```



**Installation**

Stable version from CRAN:

```{r, results='asis', echo=FALSE}
cat("```r\n")
cat("install.packages(\"",package_name,"\")", sep = "")
cat("\n```\n")
```


<!-- Latest development version from Github: -->

<!-- ```{r, eval=FALSE} -->
<!-- devtools::install_github("user_name/repo_name") -->
<!-- ``` -->



**Usage**

*starting up ...*
```{r, results='asis', echo=FALSE}
cat("```\n")
cat("library(\"",package_name,"\")", sep = "")
cat("\n```\n")
```

```{r, eval=FALSE}
cal_data <- 
  caldav_get_all_simple_auth(
    url = "https://nextcloud03.webo.cloud/remote.php/dav/calendars/usah_nameahh/personal/",
    user = "usah_nameahh",
    password =  "*********"
  )

cat(cal_data$calendar[1])
## BEGIN:VCALENDAR
## CALSCALE:GREGORIAN
## VERSION:2.0
## PRODID:-//IDN nextcloud.com//Calendar app 2.0.3//EN
## BEGIN:VEVENT
## CREATED:20200904T111126Z
## DTSTAMP:20200907T200537Z
## LAST-MODIFIED:20200907T200537Z
## SEQUENCE:3
## UID:8d9e7fb1-ea44-4986-80bb-ab009924c27e
## DTSTART;TZID=Europe/Berlin:20200904T140026
## DTEND;TZID=Europe/Berlin:20200904T150026
## SUMMARY:Whatever
## RRULE:FREQ=WEEKLY;BYDAY=FR,WE
## END:VEVENT
## BEGIN:VTIMEZONE
## TZID:Europe/Berlin
## BEGIN:DAYLIGHT
## TZOFFSETFROM:+0100
## TZOFFSETTO:+0200
## TZNAME:CEST
## DTSTART:19700329T020000
## RRULE:FREQ=YEARLY;BYMONTH=3;BYDAY=-1SU
## END:DAYLIGHT
## BEGIN:STANDARD
## TZOFFSETFROM:+0200
## TZOFFSETTO:+0100
## TZNAME:CET
## DTSTART:19701025T030000
## RRULE:FREQ=YEARLY;BYMONTH=10;BYDAY=-1SU
## END:STANDARD
## END:VTIMEZONE
## END:VCALENDAR  
```

